The perceptual dimensions of \\ sonority-driven epenthesis

### 2013-09-18 paper.tex
Added some missing citations

\ex. \textsc{Ident(SonAngle)}$<n$: Assign a violation mark if the consonants in two strings C\textsubscript{1}C\textsubscript{2} and C\textsubscript{1}VC\textsubscript{2} 
stand in correspondence, and the sonority angle between C\textsubscript{1}C\textsubscript{2} and C\textsubscript{1}V is greater than $n$. % TODO: change to it being a property of C1?

@@

Observe that of the two desiderata for such a metric, {\sc Sonority Rise} fulfills the first but not the second. Consider the falling sonority clusters. RN, NF and FT, which all have a sonority distance of -1, have a smaller {\sc Sonority Rise} than NT and RF, with a sonority distance of -2, followed by RT with a sonority distance of -3. %TODO: check if these should be + or -

@@

    \node (axisstart) at (0.5 * 15,-1) {};
    \node (axisend)   at (2.6 * 15,-1) {};
    \draw (axisstart) -- (axisend);
   \node (xaxislabel) at (2.6 * 15,-2.5) {\textsc{Sonority Angle}};

@@

  \node (2pointlabel) at (2.43 * 15,-1.5) {2.3};

    \end{tikzpicture} %TODO : draw arrow and mark 1.0, 1.5, 2.0, 2.5

@@

    \end{tikzpicture} % TODO: draw arrow and mark 1.0, 1.5, 2.0, 2.5
 \end{center}

@@

%TODO : Syllable Contact and Sonority Sequencing should not be in smallcaps unless referred to as SyllCon and SonSeq.

@@

  \ex. \label{idiolects} The four idiolects: % TODO: ref
       \a. \label{idiolecta} \tickYes OVO, \tickNo rVN \newline % \textsc{SonSeq} $\gg$ \textsc{SyllCon} $\gg$ \textsc{Dep-IO} $\gg$ \textsc{*R-Son} \newline
           [\textipa{k1rm}], [\textipa{s1B1r}], [\textipa{k1ft}], [\textipa{k1t1f}], [\textipa{s1g1d}]
       \b. \label{idiolectb} \tickYes OVO, \tickYes rVN \newline %\label{idiolectc} \textsc{SonSeq, *R-Son} $\gg$ \textsc{SyllCon} $\gg$ \textsc{Dep-IO} \newline
           [\textipa{k1r1m}], [\textipa{s1B1r}], [\textipa{k1ft}], [\textipa{k1t1f}], [\textipa{s1g1d}]
       \c. \label{idiolectc} \tickNo OVO, \tickNo rVN \newline %\label{idiolectb} \textsc{SyllCon} $\gg$ \textsc{Dep-IO} $\gg$ \textsc{SonSeq, *R-Son} \newline
           [\textipa{k1rm}], [\textipa{s1B1r}], [\textipa{k1ft}], [\textipa{k1tf}], [\textipa{s1gd}]
       \d. \label{idiolectd} \tickNo OVO, \tickYes rVN \newline %\label{idiolectd} \textsc{*R-Son} $\gg$ \textsc{SyllCon} $\gg$ \textsc{Dep-IO} $\gg$ \textsc{SonSeq} \newline
           [\textipa{k1r1m}], [\textipa{s1B1r}], [\textipa{k1ft}], [\textipa{k1tf}], [\textipa{s1gd}]

@@

\ex. /\textipa{s@B-m}/ $\rightarrow$ \textipa{s@B1m} `people-{\sc emph}'  % TODO: ref

The only clusters that give us evidence of this are /\textipa{Bm}/ clusters. These are not seen root-internally due to a high-ranking OCP effect. % TODO: ref: Greenberg cited in Rose
I suggest that there might be an undominated markedness constraint against this cluster -- either OCP(labial) or another constraint based on articulatory or perceptual difficulty -- that outranks all relevant faithfulness constraints.

@@

\ex. Align-Left: every consonant must be aligned with the left edge of some prosodic word. % TODO: cite

>>>>

\ex. \textsc{Ident(SonAngle)}$<n$: Assign a violation mark if the consonants in two strings C\textsubscript{1}C\textsubscript{2} and C\textsubscript{1}VC\textsubscript{2} 
stand in correspondence, and the sonority angle between C\textsubscript{1}C\textsubscript{2} and C\textsubscript{1}V is greater than $n$.

@@

Observe that of the two desiderata for such a metric, {\sc Sonority Rise} fulfills the first but not the second. Consider the falling sonority clusters. RN, NF and FT, which all have a sonority distance of -1, have a smaller {\sc Sonority Rise} than NT and RF, with a sonority distance of 2, followed by RT with a sonority distance of 3.

@@

    \node (axisstart) at (0.5 * 15,-1) {};
    \node (axisend)   at (2.6 * 15,-1) {};
    \draw (axisstart) -- (axisend);
   \node (xaxislabel) at (2.4 * 15,-2.4) {\textsc{Sonority Angle}};

@@

  \path [line] (2 * 15, -1.3) -- (2 * 15, -0.7) -- cycle;
  \path [line] (1 * 15, -1.3) -- (1 * 15, -0.7) -- cycle;
  \node (1mark) at (1 * 15, -1.7) {1};
  \node (2mark) at (2 * 15, -1.7) {2};

  \node (2pointlabel) at (2.43 * 15,-1.7) {2.3};

    \end{tikzpicture}

@@

@@

@@

  \ex. \label{idiolects} The four idiolects: \citep[(43)]{rose.2000}
       \a. \label{idiolecta} \tickYes OVO, \tickNo rVN \newline % \textsc{SonSeq} $\gg$ \textsc{SyllCon} $\gg$ \textsc{Dep-IO} $\gg$ \textsc{*R-Son} \newline
           [\textipa{k1rm}], [\textipa{s1B1r}], [\textipa{k1ft}], [\textipa{k1t1f}], [\textipa{s1g1d}]
       \b. \label{idiolectb} \tickYes OVO, \tickYes rVN \newline %\label{idiolectc} \textsc{SonSeq, *R-Son} $\gg$ \textsc{SyllCon} $\gg$ \textsc{Dep-IO} \newline
           [\textipa{k1r1m}], [\textipa{s1B1r}], [\textipa{k1ft}], [\textipa{k1t1f}], [\textipa{s1g1d}]
       \c. \label{idiolectc} \tickNo OVO, \tickNo rVN \newline %\label{idiolectb} \textsc{SyllCon} $\gg$ \textsc{Dep-IO} $\gg$ \textsc{SonSeq, *R-Son} \newline
           [\textipa{k1rm}], [\textipa{s1B1r}], [\textipa{k1ft}], [\textipa{k1tf}], [\textipa{s1gd}]
       \d. \label{idiolectd} \tickNo OVO, \tickYes rVN \newline %\label{idiolectd} \textsc{*R-Son} $\gg$ \textsc{SyllCon} $\gg$ \textsc{Dep-IO} $\gg$ \textsc{SonSeq} \newline
           [\textipa{k1r1m}], [\textipa{s1B1r}], [\textipa{k1ft}], [\textipa{k1tf}], [\textipa{s1gd}]

@@

\ex. /\textipa{s@B-m}/ $\rightarrow$ \textipa{s@B1m} `people-{\sc emph}'  \citep[fn. 16]{rose.2000}

The only clusters that give us evidence of this are /\textipa{Bm}/ clusters. These are not seen root-internally due to a high-ranking OCP effect \citep[cited in \citep{rose.2000}]{greenberg.1950}.
I suggest that there might be an undominated markedness constraint against this cluster -- either OCP(labial) or another constraint based on articulatory or perceptual difficulty -- that outranks all relevant faithfulness constraints.

@@

\ex. Align-Left: every consonant must be aligned with the left edge of some prosodic word. \citep[(21)]{rose.2000}
